EDIpack: A generic and interoperable Lanczos-based solver for quantum impurity problems

### 2025-07-15 Reply_RefereeB.md

*“From a computational perspective, constructing a symmetry sector amounts to defining an injective map $\mathcal{M} : \mathcal{S}_{\vec{Q}} \rightarrow \mathcal{F}_e$ that relates the consecutive indexing of the electronic states |i\rangle within a given symmetry sector $\mathcal{S}_{\vec{Q}}$ to the Fock states $|I_e\rangle$ in the electronic Fock space in their number representation. This map is typically implemented as a rank-1 integer array, whose size corresponds to the dimension of the sector $D^{\mathcal{S}}$.”*

This new formulation replaces the previous wording and makes explicit the distinction between the consecutive indexing of the sector states $|i\rangle$ and the Fock states in the integer-based occupation number representation $|I_e\rangle$. In doing so, we clarify that the mapping $\mathcal{M}$ is what connects the two encodings of the same physical state. We believe the revised text should eliminate the ambiguity the referee noted.

> *The motivation of including the code on p. 12 is unclear. What is the intention here?*

We thank the referee for raising this point. The code snippet on page 12 was originally included to illustrate the concrete implementation of the mapping from Fock states to symmetry sectors for different values of ${\tt ed\_mode}$. Our goal was to make explicit the internal logic used to construct the quantum number-conserving subspaces, bridging the gap between formal description and practical realization. Moreover, this code snippet is useful to understand the structure of the ${\tt sparse_map}$ used to implement fast algorithm for the evaluation of the reduced impurity density matrix in Section 3.5.2.

@@

We recognise that the earlier reference to the global share was misleading and ultimately unnecessary concept that we have chosen to eliminate for clarity.

The issue at hand concerns the parallel construction of a matrix that is distributed across multiple threads or MPI processes. In such a setting, each thread is responsible for computing and storing only a subset—or "chunk" ${\tt Q}$—of the full matrix, typically defined as a range of contiguous rows. To maintain consistency with the global indexing of the matrix, while allowing each thread to work independently and with locally indexed arrays, a mapping must be established between global and local indices.

The variables ${\tt istart}$ and ${\tt iend}$ define the global index range of matrix rows assigned to a given thread or process. That is, a given thread will handle only the rows from ${\tt istart}$ to ${\tt iend}$ (inclusive), corresponding to its local share of the full matrix. The variable ${\tt ishift}$ is then used to translate global row indices into local ones, effectively setting ${\tt ishift = mpiRank*Q}$. This allows local arrays to be aligned correctly with the globally defined matrix structure.

While the code is written in Fortran, this construction is not specific to the language itself. Rather, it is a general approach for handling parallel matrix distribution in any programming environment where the global matrix is divided into row blocks across multiple processing units. To avoid potential confusion and to make the implementation choices more transparent to the reader in the revised, we now write:

"*In a parallel setting, each thread is assigned a contiguous block of matrix rows $Q=D_{\mathcal S}/N_{cpu}$. We denote the locally stored rows on a given thread by $q = 1, \ldots, Q$, and relate them to their corresponding global indices $i = 1, \ldots, D_{\mathcal S}$ via the variables \texttt{istart}, \texttt{iend}, and \texttt{ishift}. Here, \texttt{istart} and \texttt{iend} define the global index range $[q_1, q_Q]$ assigned to the thread, corresponding to $q_1 = \texttt{istart}$ and $q_Q = \texttt{iend}$. The variable \texttt{ishift} $= \texttt{istart} - 1$ allows mapping between the local index $q$ and the global index $i$ through the simple relation $i = q + \texttt{ishift}$. This mapping ensures consistent global indexing while enabling efficient local computation.*"

@@

> *p. 16: GFmatrix is said to be a critical component for high-speed execution. Maybe it could be describe in more detail? In what way is it efficient? What does it mean it is multi-layed? In passing, it would be nice if the capitalization would be uniform, e.g. GFmatrix vs. gfmatrix (I understand that Fortran compiler does not care, but the human reader perhaps does).*

We thank the referee for pointing out the need for a clearer and more detailed description of the ${\tt gfmatrix}$ type, which indeed plays a central role in the performance of the code. In response, we have revised the corresponding section of the manuscript (page 16) to provide a more precise explanation of its structure and efficiency features.

The term multi-layered refers to the hierarchical organization of the ${\tt gfmatrix}$ object, which is essential for storing and accessing the analytic structure of correlation functions, i.e. the weights and the poles, in a flexible and scalable way. 
Specifically, the data are organized across three conceptual layers: (1) the many-body eigenstates of the Hamiltonian spectrum, (2) the amplitude channels associated to each such state, and (3) the set of poles and weights corresponding to physical excitations from this state. This structure is necessary to correctly represent the Lehmann decomposition of Green's functions and related objects, while still allowing dynamic access and manipulation during calculations.

The efficiency of ${\tt gfmatrix}$ stems from two main features. First, correlation functions do not need to be precomputed and stored on fixed frequency or time grids; instead, their values are computed on-the-fly at arbitrary complex arguments, allowing precise and flexible evaluation as required by different solvers or output formats. Second, memory usage is optimized by avoiding redundant storage. The internal design separates spectral data, and evaluation logic, allowing minimal overhead during the object construction and easing post-processing analysis. 
We also recognize that the use of the term "high-performance" could be misleading and rephrases the paragraph on page 16 in a more precise way as

"*The module ${\tt ED\_GFMATRIX}$ implements the class ${\tt gfmatrix}$, which provides an efficient and flexible representation of DCFs. It is structured as a hierarchical, or {\it multilayered}, data container that organizes spectral weights and poles across three levels: (i) the initial eigenstate $|n\rangle$ of the Hamiltonian spectrum, (ii) the amplitude channel associated with this state, corresponding to the applied operator, and (iii) the set of excitations from $|n\rangle$, each characterized by a pole and its corresponding weight.  
This structure allows the ${\tt gfmatrix}$ class to simultaneously handle multiple initial states and operators, enabling on-the-fly evaluation of DCFs at arbitrary complex frequencies $z \in \mathbb{C}$. By avoiding precomputed grids and redundant storage this approach minimizes memory footprint and computational overhead. As a result, ${\tt gfmatrix}$ is a core component of EDIpack, essential for efficient memory management, consistent storage of spectral data, and high-performance post-processing.*"

@@

We thank the referee for this  observation. It is indeed correct that the general strategy presented for computing off-diagonal DCFs, as described on page 21, involves constructing linear combinations of operators, which in the most general case would require working with complex-valued floating point arithmetic—even if the Hamiltonian itself is real.

However, in the special case where the Hamiltonian is real and symmetric, the resulting Green's functions are symmetric under exchange of orbital indices, i.e., $G_{\alpha\beta}(z) = G_{\beta\alpha}(z)$. This property can be exploited to compute off-diagonal elements using only real-valued linear combinations of operators. In such cases, all required DCFs can be obtained exploiting memory advantages of real-valued computations.

In the revised manuscript we clarify this point by writing in the **normal** paragraph of the section 3.8:

"*The sector Hamiltonian matrix in this mode is assumed 
to be real symmetric, which simplifies the evaluation 
of the off-diagonal terms by exploiting the following symmetry 
under orbital exchange $G_{\alpha\beta\sigma\sigma}(z)=G_{\beta\alpha\sigma\sigma}(z)$. 
In this case, the off-diagonal Green's function components can be obtained using just real-valued auxiliary operators such as  
${\mathcal O}=c_{\alpha\sigma}+c_{\beta\sigma}$, along with the identity 
$G_{\alpha\beta\sigma\sigma}=\tfrac{1}{2}(C_{\mathcal O} - G_{\alpha\alpha\sigma\sigma} - G_{\beta\beta\sigma\sigma})$,
where $C_{\mathcal O}$ denotes the DCF associated to ${\mathcal O}$. This approach, avoiding the need for complex arithmetic, preserves the efficiency of real-valued computation.*"

@@

> *In Eq. (18), is Z the same on both sides of approximation sign?*

We are indebted with the referee for pointing out this important subtlety, which in fact extends to both sections 3.8 and 3.9. In the original version of the manuscript, the partition function $Z$ appearing in different expressions (including the Eq.(18) indicated by the referee), may have misleadingly suggested that it was being evaluated exactly, even though the trace had been truncated.

In the revised manuscript we have corrected this issue. We now use the symbol $Z$ to indicate the exact partition function and reserve the symbol $\tilde{Z}$ to explicitly indicate the partition function approximated using only the finite set of low-energy eigenstates retained in the trace, i.e., those contributing significantly due to their large Boltzmann weights. This makes the approximation consistent on both sides of the involved equations, namely Eqs. (13), (14) and (18), properly reflecting the finite-state summation used in practice.

@@

> *p. 28: "as the nonsu2 and superc diagonalizations entail nontrivial subtleties in optimizing the off-diagonal components of X". What are these subtleties?*

We acknowledge that our brief comment reads a bit obscure while this point requires a more detailed, yet brief, discussion.

The bath optimization is a crucial step in the DMFT framework. As we discuss in the manuscript, to preserve the general application of EDIpack we introduced several control parameters for the conjugate-gradient fit. A key one is the definition of the norm, or distance, between matrix functions appearing in Eq. 30.

While for matrix functions with a particularly symmetric structure the choice of the metric is inessential, it might dramatically affect the quality of the optimization in more general cases. 
The subtleties in optimizing the off-diagonal components in either ${\tt nonsu2}$ and ${\tt superc}$ diagonalizations arise from the complex interplay between these components’ physical characteristics and the picked optimization metric. 
In either case, the coexistence of components having a very different physical interpretation, e.g., anomalous terms, and/or spanning very different energy scales represents a serious challenge to the optimization of the bath. 
This requires careful tuning of the control parameters to ensure that the optimization does not disproportionately favor certain matrix elements over others, thereby maintaining the overall fidelity of the bath representation.
In this sense, introducing other norms, which ensure a better balance among the components, is a development line to improve EDIpack usage.

In the revised manuscript we amended this unclear statement writing:
*"We plan to expand the available options for the cg_norm parameter in future EDIpack updates, since the nonsu2 and superc diagonalization modes involve subtle challenges in optimizing the off-diagonal components of X, due to the coexistence of matrix elements with different physical meanings and energy scales, which require carefully balanced optimization metrics to ensure an accurate bath representation."*

@@

> *As a general coding comment: would it be possible to remove use of global variables?*

We thank the referee for this general but important observation. In principle, it is indeed possible to eliminate the use of global variables by explicitly passing all data structures through subroutine arguments. However, in the context of Fortran, and similarly in other compiled languages, global variables (typically implemented via module-level variables) do not incur any performance or memory management penalties.

Their use in EDIpack is deliberate and serves to maintain clarity and modularity in the code, particularly for widely shared objects such as configuration parameters, system-wide operators, or state indexing data. Removing these global definitions would require passing a large number of arguments through deep call chains, which we believe would significantly increase code complexity, reduce readability, and introduce greater potential errors, without offering any computational or architectural advantages.

However, we recognise the importance of careful design in managing global memory, and we have ensured that such variables are encapsulated within dedicated modules with well defined scopes. Should it prove beneficial for future code maintainability or extension by third-party contributors, we are ready to review and refine this aspect of the implementation.

@@

> *p. 40: I find the discussion of parallelism in Julia wrapper unnecessary. Such information does not necessarily age well. This belongs to a readme file.*

We thank the referee for this suggestion. We agree that the detailed discussion of parallelism integration within the Julia wrapper is better suited for specialized documentation such as a README file or the on-line user manual rather than the main manuscript. Accordingly, we have removed the entire paragraph from the revised version to keep the presentation focused and ensure the manuscript’s longevity and clarity. Relevant implementation details regarding MPI usage in Julia will be provided in the package documentation to better serve users requiring this information.

> *p. 41: The code listing mentions Wband and de, but I don't see where this is coming from.*

We thank the referee for carefully reviewing this section and pointing this out. Indeed, the variable ${\tt Wband}$ should not appear in the code listing, as it corresponds to ${\tt D}$, which is correctly defined earlier in the script.  Additionally, the variable ${\tt de}$ represents the energy grid spacing, computed as ${\tt de = 2D / Le}$, where Le is the number of energy points discretizing the Bethe lattice density of states. We have corrected the code listing accordingly to eliminate Wband and clarify the definition of de.

@@

> *p. 42: "provides access to well-tested functions". This is unclear. Functions doing what?*

We thank the referee for pointing out the ambiguity in this sentence. Our intention was to clarify that, although the bath optimization problem is conceptually distinct from the core impurity diagonalization task, for which EDIpack was originally developed, nonetheless the package provides access to a well-tested implementation of the conjugate-gradient fitting procedure for the bath optimization. We have revised the sentence accordingly in the manuscript to make this connection and the role of these functions more explicit by writing:

### 2025-07-15 02_install.tex
Further tweaks in the installation section: cmake flags have changed

  -D{\bf LONG\_PREFIX}          & Install directory (if & {\color{xkcdEmerald} $\sim$/opt/edipack/\textbackslash}\\
  &install prefix unset)&{\color{xkcdEmerald}TAG/\textbackslash} (\textit{e.g. 5.3.3})\\
  &&{\color{xkcdEmerald}PLAT/\textbackslash} (\textit{gnu/intel/...})\\
  &&{\color{xkcdEmerald}BRANCH} (\textit{main/debug/...})\textbf{/}\\
  &&$\sim$/opt/edipack/custom \\
  -D{\bf USE\_MPI}       & MPI support  &  True\textbf{/}{\color{xkcdEmerald}False}\\
  -D{\bf WITH\_INEQ}   & Multi-impurities support & {\color{xkcdEmerald}True}\textbf{/}{False}\\
  -D{\bf VERBOSE}      & Verbose CMake output & {\color{xkcdEmerald}True}\textbf{/}{False}\\ 
  -D{\bf BUILD\_TYPE} & Compilation flags & {\color{xkcdEmerald}RELEASE}\textbf{/}TESTING\textbf{/}DEBUG \\
 \hline
\end{tabular}
\end{center}
%
The default target builds and installs both the main library and the C-bindings.
Separate build targets for each component are available. A recap message is printed at the end of the CMake configuration step to guide the user through the compilation, installation and OS loading process.

\subsubsection{Anaconda}
Installation is also available through Anaconda packages for Linux and macOS systems, within a virtual environment containing Python
($\geq$ 3.10).
%
The Conda package installation procedure for a virtual environment called {\tt myenv} reads
\begin{lstlisting}[style=mybash,numbers=none]
conda create -n myenv
conda activate myenv
conda install -c conda-forge -c edipack edipack
\end{lstlisting}
and installs a bundle of SciFortran and \NAME libraries together with
specific {\tt pkg-config} configuration files, which can be used to
retrieve compilation and linking flags. In order to compile Fortran/C++ 
drivers, the {\tt compilers} conda package will need to be installed.

\subsection{Environment Variables}\label{sSecInstallOSloading}
In order to avoid possible conflicts or the requirement for administrative
privileges, the results of the building step are installed by default in user's {\tt HOME}
directory, specified by the CMake variable {\tt PREFIX}.
As a consequence, the environment variables holding the library and include paths will need to be updated by the user.
We offer different ways to perform this action:
\begin{enumerate}
\item  A CMake-generated configuration file for an environment module which allows users to load and unload the library at any time. This is
  preferred solution for HPC systems. 
\item A CMake-generated bash script to be sourced (once or
  permanently) in any shell session to add \NAME library to the
  default environment.
\item A CMake generated {\tt pkg-config} file to be added in
  the {\tt PKG\_CONFIG\_PATH} itself.  
\end{enumerate}
A recap message with all instructions is automatically generated at the end of the installation procedure.

>>>>

  -D{\bf LONG\_PREFIX}          & Install directory (if & {\color{xkcdEmerald} $\sim$/opt/edipack/\textbackslash}\\
  &install prefix unset)&{\color{xkcdEmerald}TAG/\textbackslash} (\textit{e.g. 5.3.3})\\
  &&{\color{xkcdEmerald}PLAT/\textbackslash} (\textit{gnu/intel/...})\\
  &&{\color{xkcdEmerald}BRANCH} (\textit{branch name})\textbf{/}\\
  &&$\sim$/opt/edipack/custom \\
  -D{\bf USE\_MPI}       & MPI support  &  True\textbf{/}{\color{xkcdEmerald}False}\\
  -D{\bf WITH\_INEQ}   & Multi-impurities support & {\color{xkcdEmerald}True}\textbf{/}{False}\\
  -D{\bf VERBOSE}      & Verbose CMake output & {\color{xkcdEmerald}True}\textbf{/}{False}\\ 
  -D{\bf BUILD\_TYPE} & Compilation flags & {\color{xkcdEmerald}RELEASE}\textbf{/}TESTING\textbf{/}DEBUG \\
 \hline
\end{tabular}
\end{center}
%
The default target builds and installs both the main library and the C-bindings.
Separate build targets for each component are available. A recap message is printed at the end of the CMake configuration step to guide the user through the compilation, installation and OS loading process.

\subsubsection{Anaconda}
Installation is also available through Anaconda packages for Linux and macOS systems, within a virtual environment containing Python
($\geq$ 3.10).
%
The Conda package installation procedure for a virtual environment called {\tt myenv} reads
\begin{lstlisting}[style=mybash,numbers=none]
conda create -n myenv
conda activate myenv
conda install -c conda-forge -c edipack edipack
\end{lstlisting}
and installs a bundle of SciFortran and \NAME libraries together with
specific {\tt pkg-config} configuration files, which can be used to
retrieve compilation and linking flags. In order to compile Fortran/C++ 
programs, the {\tt compilers} conda package will need to be installed.

\subsection{Environment Variables}\label{sSecInstallOSloading}
In order to avoid possible conflicts or the requirement for administrative
privileges, the results of the building step are installed by default in user's {\tt HOME}
directory.
As a consequence, the environment variables holding the library and include paths will need to be updated by the user.
We offer different ways to perform this action:
\begin{enumerate}
\item  A CMake-generated configuration file for an environment module which allows users to load and unload the library at any time. This is
  preferred solution for HPC systems. 
\item A CMake-generated bash script to be sourced (once or
  permanently) in any shell session to add \NAME library to the
  default environment.
\item A CMake-generated {\tt pkg-config} file to be added in
  the {\tt PKG\_CONFIG\_PATH} itself.  
\end{enumerate}
A recap message with all instructions is automatically generated at the end of the installation procedure.

### 2025-07-15 03_edipack2.tex
Further tweaks in the installation section: cmake flags have changed

Alternatively, setting {\tt ED\_USE\_KANAMORI=F} and {\tt ED\_READ\_UMATRIX=T}, a list of two-body interaction operators can be supplied by the user in a properly
formatted text file, whose name is specified by the input variable {\tt UMATRIX\_FILE}.  
The file must have the suffix {\tt <UMATRIX\_FILE>.re\-star\-t} and should be formatted as follows: 
\begin{lstlisting}[style=mybash,numbers=none]
<NORB> BANDS
i1 j1 k1 l1 U_i1j1k1l1
i2 j2 k2 l2 U_i2j2k2l2
...
\end{lstlisting}
where {\tt NORB} is the number of orbitals $N_\a$.
Each line defines a two-body second-quantized operator of the form 
$$
\hat{H}^{\mathrm{int}}=\frac{1}{2}d^{\dagger}_{i}d^{\dagger}_{j}U_{ijkl}d_{l}d_{k}.
$$
where the indices $\{ijkl\}$ condense orbital and spin degrees of freedom, e.g. $i=\alpha\sigma$. 
Note that the coefficient indices $l$ and $k$ are swapped in the input file with respect to the two-body operator they implement. The $\tfrac{1}{2}$ prefactor is applied internally by the parsing routine and need not be accounted for by the user.
Empty lines and lines starting with {\tt \#, \%, !} are ignored.

@@

The sector Hamiltonian matrix in this mode is assumed 
to be real symmetric, which simplifies the evaluation 
of the off-diagonal terms by exploiting the following symmetry 
under orbital exchange $G_{\a\b\s\s}(z)=G_{\b\a\s\s}(z)$. 
In this case, the off-diagonal Green's function components can be obtained using just real-valued auxiliary operators such as  
$\OO=c_{\a\s}+c_{\b\s}$, along wit the identity 
$G_{\a\b\s\s}=\tfrac{1}{2}(C_\OO - G_{\a\a\s\s} - G_{\b\b\s\s})$,
where $C_\OO$ denotes the DCF associated to $\OO$      . This approach, avoiding the need for complex arithmetic, preserves the efficiency of real-valued computation.

>>>>

Alternatively, setting {\tt ED\_USE\_KANAMORI=F} and {\tt ED\_READ\_UMATRIX=T}, a list of two-body interaction operators can be supplied by the user in a properly
formatted text file, whose name is specified by the input variable {\tt UMATRIX\_FILE}.  
The file must have the suffix {\tt <UMATRIX\_FILE>.re\-star\-t} and should be formatted as follows: 
\begin{lstlisting}[style=mybash,numbers=none]
<NORB> BANDS
i1 j1 k1 l1 U_i1j1k1l1
i2 j2 k2 l2 U_i2j2k2l2
...
\end{lstlisting}
where {\tt NORB} is the number of orbitals $N_\a$.
Each line defines a two-body second-quantized operator of the form 
$$
\hat{H}^{\mathrm{int}}=\frac{1}{2}d^{\dagger}_{i}d^{\dagger}_{j}U_{ijkl}d_{l}d_{k}.
$$
where the indices $\{ijkl\}$ refer to the combined spin and internal (orbital, valley...) degrees of freedom, e.g. $i=\alpha\sigma$. 
Note that the coefficient indices $l$ and $k$ are swapped in the input file with respect to the two-body operator they implement. The $\tfrac{1}{2}$ prefactor is applied internally by the parsing routine and need not be accounted for by the user.
Empty lines and lines starting with {\tt \#, \%, !} are ignored.

@@

The sector Hamiltonian matrix in this mode is assumed 
to be real symmetric, which simplifies the evaluation 
of the off-diagonal terms by exploiting the following symmetry 
under orbital exchange $G_{\a\b\s\s}(z)=G_{\b\a\s\s}(z)$. 
In this case, the off-diagonal Green's function components can be obtained using just real-valued auxiliary operators such as  
$\OO=c_{\a\s}+c_{\b\s}$, along with the identity 
$G_{\a\b\s\s}=\tfrac{1}{2}(C_\OO - G_{\a\a\s\s} - G_{\b\b\s\s})$,
where $C_\OO$ denotes the DCF associated to $\OO$      . This approach, avoiding the need for complex arithmetic, preserves the efficiency of real-valued computation.

### 2025-07-15 04_cbinding.tex
Further tweaks in the installation section: cmake flags have changed

We provide an example script for the simple case of the Bethe lattice in the normal phase in the \secu{SecExamples} folder of the EDIpack2jl repository. This script is intended to be run serially. Documentation of the API and further examples are being developed.

>>>>

We provide an example script for the simple case of the Bethe lattice in the normal phase in the {\tt examples} folder of the EDIpack2jl repository. This script is intended to be run serially. Documentation of the API and further examples are being developed.

### 2025-07-15 06_conclusions_acknowledgement_appendix.tex
Initial Overleaf Import
Further tweaks in the installation section: cmake flags have changed

\section{Conclusions}
We have presented \NAME{}, a versatile and high-performance ED solver for generic quantum impurity problems. Building on the massively
parallel algorithms introduced by its predecessor \cite{Amaricci2022CPC}, this version of
the library features new capabilities allowing for different broken-symmetry solutions within a unified
framework that provides, for instance, reliable evaluations of a variety of local dynamical correlation
functions of an arbitrary complex frequency ranging from the Green's functions to superconducting, excitonic and magnetic response functions.

@@

\section*{Acknowledgements}
We acknowledge helpful discussions occurring at various stages of development of \NAME with: C.~Mejuto-Zaera, P.~Villar~Arribi, M.~Chatzieleftheriou, S.~Adler, M.~Collura, C.~Weber, A.~Sartori, H.~Choi, A.~Valli, M.~Rozenberg.

\paragraph{Author contributions}
A.A. designed the project, developed the main structure of the software and conceived the computational algorithms in the core library. A.A. and M.C. conceived the diagonalization, correlation function  calculation and bath optimization strategies implemented in the library. M.C. devised the inclusion of the electron-phonon coupling and of the superconducting state. 
L.C., G.M., F.P. A.S., S.G. and G.B.  equally contributed to the development and implementation of many different aspects of the  software, including code writing, configuration, installation, testing and continuous integration procedures. 
L.C. devised and developed the C-binding layer, the Python, Julia and Monicelli interface together with Python specific deployment and installation tools. 
I.K. developed the TRIQS interface and contributed to the testing part. 
A.K., M.W. and G.S. developed the integration with w2dynamics.  
A.A., M.C., L.d.M. and G.S designed additional algorithms for extended functionalities of the core software.   
A.A., L.C., I.K., A.K., S.G. and G.B. performed the calculations, analyzed the results and prepared the data presentation in the examples.
A.A. and L.C. wrote the backbone of the manuscript.
All authors participated in writing this manuscript.

% TODO: include funding information
\paragraph{Funding information}
L.C. acknowledges support from Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) thr\-ough the cluster of excellence ``CUI: Advanced Imaging of Matter" of the Deutsche Forschungsgemeinschaft (DFG EXC 2056, Project ID 390715994) and gratefully acknowledges the scientific support and HPC resources provided by the Erlangen National High Performance Computing Center (NHR@FAU) of the Friedrich-Alexander-Universität Erlangen-Nürnberg (FAU) under the NHR project b158cb. NHR funding is provided by federal and Bavarian state authorities. NHR@FAU hardware is partially funded by the German Research Foundation (DFG)– 440719683.
I.K. acknowledges support from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~854843-FASTCORR).
G.S. and A.K. acknowledge financial support by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) through FOR 5249 (project-id 449872909, Project P05), and the W\"urzburg-Dresden Cluster of Excellence on Complexity and Topology in Quantum Matter-ct.qmat (EXC 2147, project-id 390858490).
F.P. acknowledges support from the Swiss National Science Foundation via NCCR Marvel and SNSF Grant No. 200021-196966.
M.W. acknowledges support from the Austrian Science Fund (FWF) through grant DOI 10.55776/P36332.
%G.M.
G.M. acknowledges support from the MUR - Italian Ministry of University and Research - through the Rita-Levi Montalcini program.
L.dM. acknowledges support by the European Commission through the ERC-CoG2016, StrongCoPhy4Energy, GA No. 724177.
M.C., S.G. and G.B. acknowledge financial support from the National Recovery and Resilience Plan PNRR
MUR Project No.~CN00000013-ICSC and by MUR via PRIN 2020 (Prot.~2020JLZ52N-002) and PRIN 2022 (Prot.~20228YCYY7) programmes.
A.A. and M.C. acknowledge financial support from the National Recovery and Resilience Plan PNRR MUR Project No.~PE0000023-NQSTI.

>>>>

\section{Conclusions}\label{SecConclusions}
We have presented \NAME{}, a versatile and high-performance ED solver for generic quantum impurity problems. Building on the massively
parallel algorithms introduced by its predecessor \cite{Amaricci2022CPC}, this version of
the library features new capabilities allowing for different broken-symmetry solutions within a unified
framework that provides, for instance, reliable evaluations of a variety of local dynamical correlation
functions of an arbitrary complex frequency ranging from the Green's functions to superconducting, excitonic and magnetic response functions.

@@

\section*{Acknowledgements}
We acknowledge helpful discussions occurring at various stages of development of \NAME with: C.~Mejuto-Zaera, P.~Villar~Arribi, M.~Chatzieleftheriou, S.~Adler, F.~Paoletti, M.~Collura, C.~Weber, A.~Sartori, H.~Choi, A.~Valli, M.~Rozenberg.

\paragraph{Author contributions}
A.A. designed the project, developed the main structure of the software and conceived the computational algorithms in the core library. A.A., L.C. and M.C. conceived the diagonalization, correlation function  calculation and bath optimization strategies implemented in the library. A.A., G.M., A.S., S.G. and M.C. devised the inclusion of the electron-phonon coupling and of the superconducting state. 
L.C., G.M., F.P. A.S., S.G. and G.B. equally contributed to the development and implementation of many different aspects of the software, including code writing, configuration, installation, testing and continuous integration procedures. 
L.C. devised and developed the C-binding layer, the Python, Julia and Monicelli interface together with Python specific deployment and installation tools. 
I.K. developed the TRIQS interface and contributed to the testing part. 
A.K., M.W. and G.S. developed the integration with w2dynamics.  
A.A., M.C., L.d.M. and G.S designed additional algorithms for extended functionalities of the core software.   
A.A., L.C., I.K., A.K., S.G. and G.B. performed the calculations, analyzed the results and prepared the data presentation in the examples.
A.A. and L.C. wrote the backbone of the manuscript.
All authors participated in writing this manuscript.

% TODO: include funding information
\paragraph{Funding information}
L.C. acknowledges support from Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) thr\-ough the cluster of excellence ``CUI: Advanced Imaging of Matter" of the Deutsche Forschungsgemeinschaft (DFG EXC 2056, Project ID 390715994) and gratefully acknowledges the scientific support and HPC resources provided by the Erlangen National High Performance Computing Center (NHR@FAU) of the Friedrich-Alexander-Universität Erlangen-Nürnberg (FAU) under the NHR project b158cb. NHR funding is provided by federal and Bavarian state authorities. NHR@FAU hardware is partially funded by the German Research Foundation (DFG)– 440719683.
I.K. acknowledges support from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~854843-FASTCORR).
G.S. and A.K. acknowledge financial support by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) through FOR 5249 (project-id 449872909, Project P05), and the W\"urzburg-Dresden Cluster of Excellence on Complexity and Topology in Quantum Matter-ct.qmat (EXC 2147, project-id 390858490).
F.P. acknowledges support from the Swiss National Science Foundation via NCCR Marvel and SNSF Grant No. 200021-196966.
M.W. acknowledges support from the Austrian Science Fund (FWF) through grant DOI 10.55776/P36332.
G.M. acknowledges support from the MUR - Italian Ministry of University and Research - through the Rita-Levi Montalcini program.
L.dM. acknowledges support by the European Commission through the ERC-CoG2016, StrongCoPhy4Energy, GA No. 724177.
M.C., S.G. and G.B. acknowledge financial support from the National Recovery and Resilience Plan PNRR
MUR Project No.~CN00000013-ICSC and by MUR via PRIN 2020 (Prot.~2020JLZ52N-002) and PRIN 2022 (Prot.~20228YCYY7) programmes.
A.A. and M.C. acknowledge financial support from the National Recovery and Resilience Plan PNRR MUR Project No.~PE0000023-NQSTI.
